New approaches for boosting to uniformity

### 2014-10-14 assets/paperdraft/parts/metrics.tex
updated the paper draft
minor change

\subsection*{Advantages and Disadvantages of Different Metrics}
\subsubsection*{Theil and SDE}
Let us compare two metrics that have proven most appropriate for our problem, SDE and Theil. We have some masses distributed uniformly in $[0,1]$, some constant $\alpha$ from interval $[0,1]$. 
The predictions are correlated with mass via beta distribution.
First distribution with a peak is obtained by generating a prediction for each event according to its mass:
\[
	p_{\rm peak} \thicksim \text{Beta}(\alpha \mean{m}, \abs{m - \mean{m}})
\]
The second distribution is obtained by flipping:
\[
	p_{\rm pit} \thicksim 1 - \text{Beta}(\alpha \mean{m}, \abs{m - \mean{m}})
\]
SDE should show no changes if we flip the distribution, while the Theil should make difference between pit and peak.

@@

\begin{figure}[h]
\centering
	\includegraphics[width=0.9\textwidth]{graphs/TheilVsMSE.pdf}
	\caption{Comparison of SDE and Theil uniformity measures for different values of the constant $\alpha$ for the peak and pit distributions.
The Theil can clearly distinguish between these two while the SDE measure cannot.}
\end{figure}

From these figures we can see that SDE doesn't make any difference between these distributions, while Theil has lower value in the second case 
which indicates that distribution is flatter. This example demonstrates that Theil has larger penalty for distributions with narrow peaks rather than with narrow pits in the distribution of efficiecies.

>>>>

\subsection*{Advantages and Disadvantages of Different Metrics}
\subsubsection*{Theil and SDE}
Let us compare two metrics that have proven most appropriate for our problem, SDE and Theil. We have some masses distributed uniformly in $[0,1]$, some constant $\alpha$ from interval $[0,1]$. 
The predictions are correlated with mass via beta distribution.
First distribution with a peak is obtained by generating a prediction for each event according to its mass:
\[
	p_{\rm peak} \thicksim \text{Beta}(1 + \alpha f(m), 1), \qquad  f(m) = 5 \times e^{- 100  \abs{m - \overline{m}}^2}
\]
The second distribution is obtained by flipping:
\[
	p_{\rm pit} \thicksim 1 - \text{Beta}(1 + \alpha f(m), 1)
\]
SDE should show no changes if we flip the distribution, while the Theil should make difference between pit and peak.

@@

\begin{figure}[h]
\centering
	\includegraphics[width=0.9\textwidth]{graphs/TheilVsMSE.pdf}
	\caption{Comparison of SDE and Theil uniformity measures for different values of the constant $\alpha$ for the peak and pit distributions.
The Theil can clearly distinguish between these two while the SDE measure cannot.\label{fig:pitvspeak}}
\end{figure}

From figure~\ref{fig:pitvspeak} we can see that SDE doesn't make any difference between these distributions, while Theil has lower value in the second case 
which indicates that distribution is flatter. This example demonstrates that Theil has larger penalty for distributions with narrow peaks rather than with narrow pits in the distribution of efficiecies.
